# Regressions Models Course Project
In this analysis we are attempting to find out whether a manual or automatic transmission is better for miles per gallon (mpg). 

## Exploring the dataset
```{r}
library (datasets)
data(mtcars)
head(mtcars)
```

## Categorical Variables
```{r}
#Firstly vs and am should be modeled as categorical variables
mtcars$vs <- as.factor(mtcars$vs)
mtcars$am <- as.factor(mtcars$am)
```

## Summary of mpg column
```{r}
summary(mtcars$mpg)
```
## Plotting mpg for Transmission type
```{r}
boxplot(mpg ~ am, data = mtcars, xlab = "Transmission type")
```
We can see there is a significant difference between the gas mileage for each type of transmission. We will now try to fit a linear regression model.

## Simple linear regression model
```{r}
S_fit <- lm(mpg ~ factor(am), data=mtcars)
summary(S_fit)
```
We can see that the adjusted R squared value is only 0.3598 which means that only 35.98% of the regression variance can be explained by our model. Let's see how it behaves with the multivariate regression model

## Multivariable Regression Model
```{r}
data(mtcars)
M_fit <- lm(mpg ~ . ,data=mtcars)
summary(M_fit)
```
We can see that the adjusted R squared value is only 0.869 which means that 86.9% of the regression variance can be explained by our model. Now we will calculate the correlation to find which variables that along with the Transmission Type affect the outcome.

## Correlation Analysis
```{r}
cor(mtcars)[1,]
```
In addition to am, we have other variables that show high correlations. There we run the multivariate analysis with those variables as shown below.
```{r}
final_fit <- lm(mpg ~ wt+hp+disp+cyl+am, data = mtcars)
summary(final_fit)
```
We plot the residuals to check for any non-normality. 
```{r}
par(mfrow = c(2, 2))
plot(final_fit)
```


## CONCLUSION
Using the final multivariate regression model we can see the multiple R squared value is much higher at 0.8551, where 85.51% of the regression variance can be explained by the chosen variables. We can thus conclude that ‘wt’, ‘cyl’, 'disp' and 'hp' affect the outcomes of the relationship between ’am and ’mpg’.






